Articles_Plots

### 2022-11-05 Articles.Rmd
eps files saved for plots

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
```

>>>>

# ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
#   ggexport(filename = "SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
# ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
#   ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
# ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
#   ggexport(filename = "ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
# ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
#   ggexport(filename = "ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggsave(filename = "SMSE_MI_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggsave(filename = "SMSE_MI_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "ACCURACY_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggsave(filename = "ACCURACY_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
```
